Qualifying Report

### 2018-12-30 Source/QualifyingReport/QualifyingReport.tex
added source

%% TO DO LIST
% Fix the table on the literature search.
% Talk about measures of lexical diversity (TTR, Brunets, Honore's)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Document Class
\documentclass[a4paper]{article}

@@

\title{Literature Review}
\date{2018-09-05}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin {document}

@@

\section{Introduction}

@@

% In this paragraph, look for the study which actually has these figures.

@@

One of the most common ways in which clinicians traditionally make an early diagnosis of cognitive impairment is through the use of the Mini Mental State Examination (MMSE) \cite{Folstein1975}. The MMSE is a brief questionnaire consisting of eleven questions which tests cognitive aspects of mental function and requires only 5-10 minutes to administer \cite{Folstein1975}. The MMSE is chosen due to it's effectiveness at assessing a person's cognitive mental state at a specific point in time, as well as being as sensitive to changes as a more detailed and complex assessment such as the Wechler Adult Intelligence Scale \cite{Folstein1975}. Whilst the MMSE is useful as a brief screening tool it has it's limitations. The MMSE was not specifically created to screen for dementias and therefore does not interrogate key aspects of cognitive impairment known to be affected in dementia. It also has limited value in assessing under-educated subjects and a meta-analysis on the effectiveness of the MMSE as a diagnostic tool for dementia to showed that it's accuracy was low (sensitivity between 78.4\% and 85.1\% and specificity between 81.3\% and 87.8\%). As the MMSE is shown to have low accuracy specifically in the diagnosis of dementia, it becomes necessary for professionals to employ the use of other tools or measures such as the Free Cued Selective Reminding Test (FCSRT) or the Montreal Cognitive Assessment (MoCA). These tests have the benefits of being much more accurate at diagnosing cognitive impairment and discriminating between dementia and other types of cognitive impairment at the cost time and training of psychological professionals such as clinical psychologists in administering these tests. Given the burden on these professionals is likely to increase due to a growing elderly population or in the case of developing countries where the clinician / patient ratio is already unsustainable, it seems useful to find less burdensome ways to aid professionals in diagnosing dementia. \newline

@@

The two main ways in which diagnosis is performed is through assessment of memory and language. Tests of memory are classically among the most accurate ways of diagnosing dementia, however these tests suffer from the same reliance on trained clinicians to administer these tests in a clinical setting. Language however is a lot easier to collect and can be done in more naturalistic settings. As with memory, these tests can be done over time and would be able to chart a patients language degeneration over time. Given that language is less intrusive to test and requires a lot of the cognitive processes that may be impacted by AD, a lot of research has focused on measure decline in the use of language in those with AD. There are a wide number of factors that are involved in language degeneration in the elderly, and consequently there will be an expected amount of variability between subjects. The consensus is that this language degeneration is typically accelerated by the presence of dementia \cite{Berisha2015} and that a potential indicator of dementia is the rate of change in which the decline occurs relative to a fixed point in time rather than a comparison across a cohort of individuals. \newline

@@

\subsection{Aims and Methodology}
\par 
The purpose of this review is to seek to understand what techniques for assessing language have been used within the field of cognitive and clinical psychology. We then go on to look at what techniques have been developed in the field of machine learning (ML), deep learning (DL) and natural language processing (NLP) that might enable the automated analysis of language easier as well as an obstacles and/or limitations of current technology. Finally, we look at some studies which have already looked at the intersection of these two domains. \newline
\par 
A search of the literature was conducted using ProQuest (PsychArticles), SCOPUS, Web of Science. The following results were found (Table 1). All papers were then reviewed for relevance by reading the abstract and full text where appropriate and a shortlist was compiled. An additional search through references of shortlisted papers was also conducted and any papers who upon further review appeared relevant were added to the shortlist. Papers were included where researchers used machine learning to classify participants as MCI, AD or Healthy using language. We excluded any papers that focused on other forms of dementia or cognitive impairment, as well as any papers in which the language being analysed was not English. This resulted in 17 journal articles and/or conference papers which form this review.

\begin{table}
	\begin{tabular}{ | c | c | c | p{1cm} |}
		\hline
		Database & Number of Results & Search Terms  \\ \hline
		ProQuest(PsychArticles) & 1484 Results & Language AND Decline AND Dementia \\ \hline
		ProQuest(PsychArticles) & 486 Results  & Language AND Decline AND Dementia AND Speech \\ \hline
		ProQuest(PsychArticles) & 159 Results & Machine Learning AND Dementia AND Language \\ \hline
		Web of Science & 1207 Results  & Language AND Decline AND Dementia   \\ \hline
		Web of Science & 151 Results  & Language AND Decline AND Dementia AND Speech  \\ \hline
		Web of Science & 34 Results & Machine Learning AND Dementia AND Language \\ \hline
		Scopus & 791 Results & Language AND Decline AND Dementia  \\ \hline
		Scopus & 91 Results & Language AND Decline AND Dementia AND Speech   \\ \hline
		Scopus & 29 Results & Machine Learning AND Dementia AND Langauge \\ \hline
		Scopus & 1292 Results & "Language Deficits" AND Dementia \\ \hline
	\end{tabular}
	\caption{\label{tab:table-name}Search Terms and Number of Results.}
\end{table}

\section {Types of Language Assessment}

@@

\subsection{Picture Description Tasks}

@@

\subsection{Narrative description task}

@@

\subsection{Interviews}

@@

The analysis of interviews can be difficult to analyse as both the content can vary even between participants. It is also difficult to measure as there are no pre-defined task goals in comparison to the other two methods. Nevertheless, this is the most naturalistic setting for looking at language production and can be used to look at the syntactic and semantic parts of language generation \cite{Sajjadi2012}. There have been some attempts to use interviews to assess language production in AD with promising results \cite{Asgari2017, Guinn2015 .\newline

@@

\section{How do we analyse language, issues and debates}
\subsection{Single Word Language tasks vs Connected Language tasks}

@@

\subsection{Semantics vs Pragmatics}

@@

\section{Semantic Content}

@@

\subsection{Picture-related content thematic elements}

@@

\subsection{General Information Units}

@@

\subsection{Conciseness of information}

@@

\subsection{Efficiency}

@@

\subsection{Lexical richness and diversity}

@@

\subsection{Quantity - Total number of words}

@@

\section{Syntax and Morphology (Language Form)}

@@

\subsection{N-grams}

@@

\subsection{Mean length of utterance (MLU)}

@@

\subsection{Proportion of verbs to nouns plus verbs}

@@

\subsection{Syntactic Complexity - Composite measures of MLU, syntactic errors and verbs}

@@

\subsection{Formulaic Language}

@@

\section{Pragmatic Language}

@@

\subsection{Questions, turn-taking, unsure statements, egocentric comments}

@@

\subsection{Coherence}

@@

\subsection{Perseveration}

@@

\subsection{Speech intonation / prosody}

@@

\subsection{Discourse Fluency}

@@

\subsection{Speech Monitoring}

@@

\section{State of literature into Natural Language processing techniques}
As we can see, diagnosing dementia through analysis has a large background in terms of psychological research. However, a lot of more current research has called for the use of machine learning as a way of assisting in the process of diagnosis \cite{Boschi2017}. Generally speaking, Natural Language Processing (NLP) systems mimic the semiotic perspective on language. That is to say that we can subdivide NLP processes into different components. This broadly fits with the literature review conducted by Emery.
\begin{enumerate}
	\item Morphological/Lexical: providing the basic language elements or vocabulary, such as words, their roots and inflections.
	\item Syntactic: for grouping and sequencing elementds within samples of language (usually sentences).
	\item Semantic: for knowing the meaning of an utterance, usually defined in terms of the 'truth value' of the logical propositions that are thought to be expressed by sentences.
	\item Pragmatic: for understanding the context and purpose of an utterance.
\end{enumerate}
\subsection{Traditional methods of Machine Learning and Natural Language Processing}

\subsection{Deep Learning}

\section{The problems with attempting early diagnosis of dementia and the ethics of actively screening for it}

@@

\section{Conclusions and Future Work}

@@

\subsection{Future Work}

@@

\bibliographystyle{unsrt}
\bibliography{LiteratureReview}
\end {document}

>>>>

% HEADER BEGINS
\documentclass{article}

@@

\title{Qualifying Report}
\date{2018-12-18}

@@

% HEADER ENDS
% DOCUMENT BEGINS
\begin{document}

@@

\section{Overview of Problem and potential contribution.}
Dementia has been identified as one of those fast growing difficulties facing the world. A recent report suggests that in 2015 there were 46 million people with a diagnosis of dementia and that number is expected to hit 131.5 million by 2050 \cite{Prince2015}. The report also states that the worldwide cost of dementia in 2018 is estimated to be in the region of one trillion US dollars.
\newline
In 2009, the Department of Health in it's National Dementia strategy made 'early diagnosis and support' one of it's key themes as part of this strategy. With that in mind, a lot of work has gone into trying to find ways of improving the early diagnosis of Alzheimer's Disease (AD) and Mild Cogntive Impairment (MCI). As described above, the numbers of those suffering from AD and MCI are going to increase as the population ages and thus it is important that we utilise technology wherever possible to aid clinicians. At the present time diagnosis is typically conducted at memory clinics by trained clinicians. I theorise that we might be able to use diagnose patients in their own homes utilising smart-home technology.
\newline
Language analysis is an important part of assessing those suspected of suffering with AD or MCI and this language analysis in part informs an official clinical diagnosis. This analysis often takes the form of tasks such as Free Cued Selective Reminding Task and the picture description task which are all quite targeted in the language required of the person being assessed. Other studies have analysed more spontaneous samples of language and have identified patterns of speech which decline. 
\newline
A step towards the ambient detection of AD and/or MCI in population requires that we look for similar features in language used naturally as part of every day conversation. Part of this work therefore is to see whether spontaneous discourse, such a semi-structured interview is a task that has the ability to put pressure both the cognitive and linguistic systems as it requires the ability to understand speech, formulating a coherent answer and then responding in an appropriate way. Berisha et al \cite{Berisha2015}, has shown through language analysis in this area that there are marked differences in this process between those who have a diagnosis of AD and healthy controls.
\newline
The potential impact of this research is immense. Research has shown that early diagnosis of people with AD or MCI improves sufferers quality of life and can slow the progress of the disease. Equally, early diagnosis can increase the number of research opportunities for understanding the early stages of dementia and how the disease progresses so that more research can be conducted which may, in the future, lead to new treatments and other interventions.
\section{Literature Review}
\subsection{Introduction}

@@

@@

One of the most common ways in which clinicians traditionally make an early diagnosis of cognitive impairment is through the use of the Mini Mental State Examination (MMSE) \cite{Folstein1975}. The MMSE is a brief questionnaire consisting of eleven questions which tests cognitive aspects of mental function and requires only 5-10 minutes to administer \cite{Folstein1975}. The MMSE is chosen due to it's effectiveness at assessing a person's cognitive mental state at a specific point in time, as well as being as sensitive to changes as a more detailed and complex assessment such as the Wechler Adult Intelligence Scale \cite{Folstein1975}. Whilst the MMSE is useful as a brief screening tool it has it's limitations. The MMSE was not specifically created to screen for dementias and therefore does not interrogate key aspects of cognitive impairment known to be affected in dementia. It also has limited value in assessing under-educated subjects and a meta-analysis on the effectiveness of the MMSE as a diagnostic tool for dementia to showed that it's accuracy was low (sensitivity between 78.4\% and 85.1\% and specificity between 81.3\% and 87.8\%). As the MMSE is shown to have low accuracy specifically in the diagnosis of dementia, it becomes necessary for professionals to employ the use of other tools or measures such as the Free Cued Selective Reminding Test (FCSRT) or the Montreal Cognitive Assessment (MoCA). These tests have the benefits of being much more accurate at diagnosing cognitive impairment and discriminating between dementia and other types of cognitive impairment at the cost time and training of psychological professionals such as clinical psychologists in administering these tests. Given the burden on these professionals is likely to increase due to a growing elderly population or in the case of developing countries where the clinician / patient ratio is already unsustainable, it seems useful to find less burdensome ways to aid professionals in identifying those at risk of developing dementia. \newline

@@

Many researchers have studied the early detection of AD. These studies usually follow two main approaches. The analysis of biomarkers and the examination of patients who have demonstrated decreasing cognitive abilities. The first approach yields reliable results in the detection of AD in its moderate and advanced states but does not perform well during the early stages of the disease. The second approach has gained more attention in recent years, due to the fact that in clinical practice it has shown promise in the early detection of AD. In addition, the analysis of the decline of cognitive abilities is comparitively inexpensive and less invasive that the first approach which commonly requires the collection of a sample of cerebro-spinal fluid which is painful for the patient involved. /newline
/par
The two main ways in which diagnosis is performed is through assessment of memory and language. Tests of memory are classically among the most accurate ways of diagnosing dementia, however these tests suffer from the same reliance on trained clinicians to administer these tests in a clinical setting. Language however is a lot easier to collect and can be done in more naturalistic settings. As with memory, these tests can be done over time and would be able to chart a patients language degeneration over time. Given that language is less intrusive to test and requires a lot of the cognitive processes that may be impacted by AD, a lot of research has focused on measure decline in the use of language in those with AD. There are a number of difficulties to watch out for with this approach. There are a wide number of factors that are involved in language degeneration in the elderly, and consequently there will be an expected amount of variability between subjects. The administration of such tests may induce nervousness and discomfort which may impact performance, and also repeatedly administering the same language tests to tests for differences over time by be confounded by improved performance at tasks via practice effects. Also, generally speaking the language tests that are currently being used do not necessarily describe patients 'real performance' in language production. However, there is enough promise in this approach such that it could help further our understanding of the disease, it's progression and the parts of the brain affected in the early stages. \newline
The consensus is that this language degeneration is typically accelerated by the presence of dementia \cite{Berisha2015} and that a potential indicator of dementia is the rate of change in which the decline occurs relative to a fixed point in time rather than a comparison across a cohort of individuals. \newline

@@

\subsubsection{Aims and Methodology}
\par
The purpose of this review is to seek to understand what techniques for assessing language have been used within the field of cognitive and clinical psychology. We then go on to look at what techniques have been developed in the field of machine learning (ML), deep learning (DL) and natural language processing (NLP) that might enable the automated analysis of language easier as well as an obstacles and/or limitations of current technology. Finally, we look at some studies which have already looked at the intersection of these two domains. \newline
\par
A search of the literature was conducted using ProQuest (PsychArticles), SCOPUS, Web of Science. The following results were found (Table 1). All papers were then reviewed for relevance by reading the abstract and full text where appropriate and a shortlist was compiled. An additional search through references of shortlisted papers was also conducted and any papers who upon further review appeared relevant were added to the shortlist. Papers were included where researchers used machine learning to classify participants as MCI, AD or Healthy using language. We excluded any papers that focused on other forms of dementia or cognitive impairment, as well as any papers in which the language being analysed was not English. This resulted in 17 journal articles and/or conference papers which form this review.
\begin{table}
	\begin{tabular}{ | c | c | c | p{1cm} |}
		\hline
		Database & Number of Results & Search Terms  \\ \hline
		ProQuest(PsychArticles) & 1484 Results & Language AND Decline AND Dementia \\ \hline
		ProQuest(PsychArticles) & 486 Results  & Language AND Decline AND Dementia AND Speech \\ \hline
		ProQuest(PsychArticles) & 159 Results & Machine Learning AND Dementia AND Language \\ \hline
		Web of Science & 1207 Results  & Language AND Decline AND Dementia   \\ \hline
		Web of Science & 151 Results  & Language AND Decline AND Dementia AND Speech  \\ \hline
		Web of Science & 34 Results & Machine Learning AND Dementia AND Language \\ \hline
		Scopus & 791 Results & Language AND Decline AND Dementia  \\ \hline
		Scopus & 91 Results & Language AND Decline AND Dementia AND Speech   \\ \hline
		Scopus & 29 Results & Machine Learning AND Dementia AND Langauge \\ \hline
		Scopus & 1292 Results & "Language Deficits" AND Dementia \\ \hline
	\end{tabular}
	\caption{\label{tab:table-name}Search Terms and Number of Results.}
\end{table}

\subsection {Types of Language Assessment}

@@

\subsubsection{Picture Description Tasks}

@@

\subsubsection{Narrative description task}

@@

\subsubsection{Interviews}

@@

The analysis of interviews can be difficult to analyse as both the content can vary even between participants. It is also difficult to measure as there are no pre-defined task goals in comparison to the other two methods. Nevertheless, this is the most naturalistic setting for looking at language production and can be used to look at the syntactic and semantic parts of language generation \cite{Sajjadi2012}. There have been some attempts to use interviews to assess language production in AD with promising results \cite{Asgari2017, Guinn2015} .\newline

@@

\subsection{How do we analyse language, issues and debates}
\subsubsection{Single Word Language tasks vs Connected Language tasks}

@@

\subsubsection{Semantics vs Pragmatics}

@@

\subsection{Semantic Content}

@@

\subsubsection{Picture-related content thematic elements}

@@

\subsubsection{General Information Units}

@@

\subsubsection{Conciseness of information}

@@

\subsubsection{Efficiency}

@@

\subsubsection{Lexical richness and diversity}

@@

\subsubsection{Quantity - Total number of words}

@@

\subsection{Syntax and Morphology (Language Form)}

@@

\subsubsection{N-grams}

@@

\subsubsection{Mean length of utterance (MLU)}

@@

\subsubsection{Proportion of verbs to nouns plus verbs}

@@

\subsubsection{Syntactic Complexity - Composite measures of MLU, syntactic errors and verbs}

@@

\subsubsection{Formulaic Language}

@@

\subsection{Pragmatic Language}

@@

\subsubsection{Questions, turn-taking, unsure statements, egocentric comments}

@@

\subsubsection{Coherence}

@@

\subsubsection{Perseveration}

@@

\subsubsection{Speech intonation / prosody}

@@

\subsubsection{Discourse Fluency}

@@

\subsubsection{Speech Monitoring}

@@

\subsection{Existing Neuropsychological Measures of Cognitive Impairment, and Repeatable Battery of Neuropsychological Tests}
In terms of standardised cognitive tests, there are two main aims. Does the test distinguish accurately between normal aging, MCI and AD (diagnostic utility) and, does the test distinguish between those individuals with MCI who will then go on to develop AD and those individuals with MCI who don't then go on to develop AD (prognostic utility). This section of the literature review outlines a number of different cognitive tests that have been used to measure cognitive impairments as well as their perfomance in terms of both diagnostic and prognostic utility. \newline
\par 
\subsubsection{RBANS - Repeated Battery for the Assessment of Neuropsychological Status}
\subsubsection{Patient Health Questionnaire)}
\subsubsection{WASI}
\subsubsection{Digit Span}
\subsubsection{Rey Words}
\subsubsection{Prospective Memory Recall}
\subsubsection{Digit symbol coding}
\subsubsection{Corsi Span}
\subsubsection{Verbal Fluency}
%% In this paragraph cite Henry et al, 2004 - taken from Taler and Phillips (2008) - Henry et al, 2004 is a meta analysis
There are a number of tests that characterise this category of verbal fluency, but generally fall into two categories. Letter (Phonemic) fluency involves the generation of as many words as possible which begin with a specified letter. Category fluency involves the generation of as many words as possible that fall into a specfied category. Both these tasks impose demands on a number of different cognitive processes namely, executive function, verbal retrieval and recall, giving appropriate answers while monitoring previous answers and inhibit inappropriate responses. However, these two tasks require different strategies when attempting them. Letter fluency relies on search strategies based on lexical representations whereas category fluency requires a search for semantic extensions of a superordinate term, meaning that semantic associations within the lexicon must be intact in order for the task to be carried out successfully. \par  
There have been numerous studies which have documented the impact that AD has on verbal fluency tests in both categories. A review carried out by Henry et al, found that performance in both letter fluency and category fluency was impaired in those with AD vs controls, but found a larger effect for tests of semantic fluency.
\subsubsection{Rey Delayed Recall}
\subsubsection{Naming - Speeded}

\subsubsection{Wisconsin Card Sorting}
\subsubsection{Complex Figure Task immediate and delayed recall}
\subsubsection{Cinderella Story - Narrative Description}
\subsubsection{Sentence Completion}
\subsubsection{Non-word Repetition}
\subsubsection{Grooved Peg Board}
\subsubsection{Visual Search}
\subsubsection{Spelling}
\subsubsection{Continuous Picture Naming}
\subsubsection{Free Cued Selective Reminding Test}
The Free Cued Selective Reminding Test (FCSRT) was borne out of the premise that by controlling the conditions of learning, a measure of memory is possible that is not confounded by normal age related changes in cognition. Theoretically speaking, any controlled learning test should be able to discriminate between cognitive decline due to age and cogntive decline due to a cognitive impairment. /newline
/par
FCSRT-IR (The instant recall version of the Free Cued Selective Reminding Test) performance has beeen shown to distinguish patients with MCI who then went on to develop AD, from those with MCI that did not then go on to develop AD and this led the authors to define prodromal or the amnestic syndrome of the medial temporal lobe by FSCRT-IR performance (Sarazin et al, 2007 /newline
/par
The sensitivity and specificity of the different test forms in correctly classifying patients were compared to each other using a previously established FCSRT-IR cut off score. /newline
/par

\subsubsection{ Description (Cookie Theft Picture)}

\subsection{State of literature into Natural Language processing techniques}
As we can see, diagnosing dementia through analysis has a large background in terms of psychological research. However, a lot of more current research has called for the use of machine learning as a way of assisting in the process of diagnosis \cite{Boschi2017}. Generally speaking, Natural Language Processing (NLP) systems mimic the semiotic perspective on language. That is to say that we can subdivide NLP processes into different components. This broadly fits with the literature review conducted by Emery.
\begin{enumerate}
	\item Morphological/Lexical: providing the basic language elements or vocabulary, such as words, their roots and inflections.
	\item Syntactic: for grouping and sequencing elementds within samples of language (usually sentences).
	\item Semantic: for knowing the meaning of an utterance, usually defined in terms of the 'truth value' of the logical propositions that are thought to be expressed by sentences.
	\item Pragmatic: for understanding the context and purpose of an utterance.
\end{enumerate}
\subsubsection{Traditional methods of Machine Learning and Natural Language Processing}

\subsubsection{Deep Learning}

\subsection{The problems with attempting early diagnosis of dementia and the ethics of actively screening for it}

@@

\subsection{Conclusions and Future Work}

@@

\subsubsection{Future Work}

@@

\section{Project Proposal}
\textbf{Full Title of the Research:} Title here \newline
\textbf{Research Questions and Hypotheses}
The broad question is can we use Machine Learning to assist in the early diagnosis of dementia and/or mild cognitive impairment through language produced naturally rather than language that is produced as part of a formal cognitive assessment. There have been a number of studies from the psychological perspective that look at the changes in language in those with Dementia. These studies have identified a number of speech and language differences between healthy controls and those with dementia. Some of these features have been validated in work using machine learning to classify healthy controls from those with dementia. However, these have been done in lab settings, with formal cognitive assessment tasks such as the 'picture description task'. While this is help to learn that machine learning can be used to differentiate between healthy controls and those with dementia, this doesn't take the burden off healthcare professionals who have to conduct the assessments and other professionals who may be used to transcribe these assessments. \newline
\par
Machine Learning itself is undergoing a shift in focus at the present time. I will describe this shift using the context of my proposed research. In traditional machine learning, the transcripts from cognitive assessments are used to generate features such as idea density. These features are then used to classify patients. A company in Toronto, Canada has taken this approach and currently uses over 400 acoustic and language features to make this classification and to generate a psuedo MMSE score. \newline
\par
Deep Learning takes a different approach by bypassing the feature generating stage. Deep learning uses neural networks as a fundamental building block.

\subsection{Aims and Rationale}
The aim of my research is to find less burdensome ways of detecting dementia without the use of invasive procedures (taking bloods, or using medical equipment such as MRI's and EEG's) 	and without resorting to to time-consuming and expensive psychological tests. There is a lot of research into the analysis of language as a bio-marker for MCI and Early Dementia. Given 			that sampling a person's language is relatively effortless, my research looks at whether we can find bio-markers of MCI and Early Dementia in natural language.\newline
Concerns: Language and Memory are quite naturally intertwined and it would be difficult to test one without some reliance on the other. I'm not going to control for memory problems as a 			potential confound, but does this weaken the research? How do I defend this? \newline
\begin{itemize}
	\item Hypothesis. I predict that, given a number of samples of language over a given time from, is it possible to detect language decline in humans such that you can differentiate between normal language decline and decline in those with MCI.
	\item Hypothesis. I predict that my new neuropsychological battery of tests will be more sensitive at detecting mild cognitive impairment than existing measures.
	\item My first hypothesis is whether monitoring language samples and other measures of cognitive decline over the course of the year is enough to detect cognitive decline in a population of those with Subjective Cognitive Decline and Mild Cognitive Impairment.
	\item My second hypothesis is that those with MCI show a different language profile to controls, if matched similarly for education and other significant factors.
\end{itemize}	
\section{Experiment 1 - Pilot Study of Neuropsychological Tests}
\subsection{Methods}
I recruited a cohort of 9 volunteers which which to complete the battery of Neuropsychological tests. We compiled a series of tests (see literature review for a comprehensive list, explanation and rationale for each test) and completed each version of the test on three consequetive days. The results of which were compiled and analysed. The hypothesis is that there would be no difference in performance between one battery of tests and another. An additional hypothesis is that the language tasks included on each task would be enough to collect an appropriate sample for linguistic analysis, such that we may be able to detect cognitive decline in a clinical population. \newline
\subsubsection{Participants}
\subsection{Results}
\subsection{Discussion}
\subsection{Conclusion}
\section{Experiment 2 - Initial Study of the Presidents corpus}
\subsection{Background}
\subsection{Methods}
I took 46 transcripts of Ronald Reagan’s (RR) press conferences from 1981 to 1988 and compared them with 134 press conferences by George H. W. Bush (GHWB) and 25 press conferences conducted by Donald J. Trump (DJT).  I analyzed transcripts for lexical features shown to change longitudinally with dementia  (for a comprehensive review of these, see the literature review above). For this collection of documents, I generated a number of features which looked at a number of different aspects of each document. These features encompassed, word level, sentence level and document level features and included a number of features contained in the study by Berisha and Liss with the aim of replicating and extending on their findings. These findings were. number of unique words, non-specific nouns and fillers and low imageability (LI) verbs. Imageability is characterized, according to Berisha and Liss, as the ease with which a term gives rise to a sensory .mental image. I compared the trends described in the transcripts of RR and GHWB, but also included DT. Berisha and Liss originally made the comparison as it GHWB (GHWB - age at the start of presidency - 64 years, 222 days) was the closest match to RR in terms of age (RR  - age at the start of presidency, 69 yeaars and 349 days). However, with the inauguration of Trump, he now is the closest comparible president in terms of age (DJT - age at the start of presidency - 70 years, 220 days). It would be interesting to look at a comparison of RR and DJT to see whether the comparisons made by Berisha and Liss hold true with this more appropriate match (in terms of age). DJT as with GHWB has no known diagnosis of AD. I used the press conference transcripts in the American Presidency Project (APP) archive as a data source for this project. The APP is a comprehensive and organized searchable database of presidential documents, including transcripts of speeches, transcripts of news conferences, and other public documents.
\subsubsection{Pre-processing}
To generate the files necessary for analysis, I downloaded each transcript and performed the following changes. I omitted the prepared statement by the president and any speech by other individuals. I started each transcript at the beginning of the first answer to a question. I filtered any annotations that were added to the transcript, including any references or clarifications, and any laughter. It's worth noting that there appears to be a difference in how 'hesitations' were marked down between each president, for RR hesitations were marked by a single hyphen whereas for GWB hesitations are marked by a double hyphen. In order to maintain consistency when parsing through the documents, I have changed both types of hesitation to be marked by a single hyphen. I also omitted one word sentences as this data would, from a theoretical perspective, not be relevant for language analysis. I did not control for the length of the document, but generated features which would normalise by the length of the document. I therefore was able to include all press conferences by both Ronald Reagan and George H.W. Bush where there was a question and answer session conducted at least in part by the sitting president (2 press conferences of GWB were ommited due to a lack of a question and answer session).
\subsection{Results}
\subsection{Discussion}
\subsection{Conclusion}

\subsection{Timeline of Future Work and Publication plan}
\textbf{Year One} \newline
\textbf{Year Two} \newline
\textbf{Year Three} \newline

\subsection{Provisional Table of Contents}
\subsubsection{Chapter 1: Introduction}
Introduction to the problem of dementia in the context of the wider world including quality of life and financial implications. Exploration of dementia as a syndrome rather than a disease, and a look at the different variants of dementia. A look at the rationale behind research into the early diagnosis of dementia as well as a brief look at what has been done in the area (wide context, so pharmacological and psychological). \newline
\subsubsection{Chapter 2: Background}
Literature Review which looks at the background of what has been done in the area of early diagnosis of dementia, from a purely psychological perspective as well as the work done in machine learning in this topic. Look at the different attributes that researchers have explored. Look at the difference between traditional machine learning methods and deep learning and discuss the pros and cons of each perspective. \newline
\subsection{Chapter 3: Experiments with existing datasets: Presidential Press Conferences, Three Authors - Murdoch, Christie and James, DementiaBank dataset.}
Aim: To replicate and extend the work by Berisha and Liss. To use traditional machine learning techniques to test whether they can differentiate between Reagan, Bush and Trump using similar features. To test to see whether Deep Learning can also differentiate between the three. \newline
Dataset: the presidential press conferences given by Presidents Ronald Reagan, George H.W. Bush and Donald Trump. \newline
Paper: This experiment replicates work done by Berisha and Liss and extends this by adding Donald Trump as an alternative comparison to Ronald Reagan. This experiment will look at the features originally recommended by Berisha and Liss, as well as any others that have potential as discussed in the literature review above. \newline
Aim: To replicate the work by Le et al. To use traditional machine learning techniques to see if it can differentiate between the three authors using similar features. To test to see whether deep learning can also differentiate between the three. To add 'pre-trained' layers from Presidential Debates experiment to see if this improves accuracy. \newline
Dataset is the literary novels of Iris Murdoch, Agatha Christie and P.D. James. \newline
Paper:
Aim: To replicate and extend the work of Orimaye et al. To use traditional machine learning techniques to see if it can categorise people into dementia or healthy categories using the samples given. To see whether can use pre-trained layer from presidential debates to improve accuracy. It doesn't seem relevant to use pretrained layer from Experiment four, but it might be worth looking at the results of this. \newline
Dataset: The DementiaBank Corpus. \newline
Paper: To replicate and extend the work of Orimaye et al. To compare traditional machine learning techniques (already completed by Orimaye) and deep learning. \newline
\subsection{Chapter 4: Validation of new repeatable neuropsychological battery for detecting MCI.}
Aim: \newline
Dataset: To be created.

\subsection{Chapter 5: Longditunal Study }
\subsubsection{Dataset creation}
The aim is to recruit a set of 50 participants with MCI / Early Dementia (diagnosed or undiagnosed) and a set of 50 controls with a similar age and broadly similar educational background (a known potential confound in assessing cognitive decline). The rationale for recruiting this number is that there will be an expected drop out rate and so
Paper:
\subsubsection{Ethics}
Need to discuss confidentiality right at the start of each conversation and to reiterate at every meeting. I will also provide an information sheet which details the confidentiality statement. The spoken confidentiality statement will be as follows.
"Anything you say to me today will be confidential unless I feel that there is a risk to you, or someone else. If this is the case, I may need to speak to or write to third parties such as your GP. Is this ok?" \newline
\par
\subsubsection{What if someone reveals suicidal ideation or other risks?}
As part of the battery of tests for this experiment, there is an opportunity for a participant to reveal that he or she has had suicidal ideation in the past two weeks (Patient Health Questionnaire, Question 9). This is something to explore further. As I have been trained in psychological risk assessments, it seems appropriate to carry out a further risk assessment.  Optionally with the tape recorder turned on, or off as requested.  Any text recorded during the risk assessment will not be included in the language analysis. Following this, some information about local services such as Improving Access to Psychological Therapies (IAPT), Samaritans and other appropriate services will be provided. A discussion will then be made about whether it is appropriate to notify the GP of the disclosure. In the event that there is imminent risk to self or others, a discussion will be made about who I need to contact. (Crisis Team and GP). In the event that the participant scores 0 on Q9 of the PHQ, no risk assessment will be undertaken. \newline
\subsubsection{What happens at the end of the data collection phase if there is a suspected decline in a participant's cognitive function}
\subsection{How does language differ between those with AD, MCI and Controls}
\subsection{Chapter 7: Overall results and Discussion}
\subsection{Chapter 8: Conclusions and Future work}

\bibliographystyle{unsrt}
\bibliography{QualifyingReport.bib}

\appendix
\section{Title of Appendix A}
Text of Appendix A is Here

\section{Title of Appendix B}
Text of Appendix B is Here

\section{Title of Appendix C}
Text of Appendix C is Here.

\end{document}
%DOCUMENT ENDS
